Pillar 1 - Sequential Pattern Mining

### 2019-02-21 Pillar 1 - Sequential Pattern Mining.Rmd
filter rules for course recommender app

  # reduce number of rules
  filter(
    lhs_course  != rhs_course, # exclude rules with same course on lhs and rhs
    rhs_outcome == 6            
    ) %>%

  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
  group_by(
    lhs_course, 
    rhs_course
    ) %>%
  top_n(
    1,
    lift
    ) %>%
  ungroup
```

@@

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
filter_rules <- function(rules){

@@

    filter(
      count      >= 10,
      lift       >= 1,
      confidence >= 0.4
      )

@@

```{r edit rules}
AR <- lapply(
  X   = AR,
  FUN = filter_rules
  )

@@

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/rules/rules.RDATA"
  )

save(
  AR, SR,
  file = "App/Recommender System/rules.RDATA"
  )
```

>>>>

@@

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules <- function(rules){

@@

    select(
      lhs, rhs,
      support, count,
      confidence,
      matches("rhsTake.support"),
      lift,
      matches("rhsTake.count")
      ) %>%

     mutate_if(
       is.numeric,
       round,
       digits = 3
       ) %>%

    arrange(
      desc(count)
      )

@@

```{r edit rules}
AR <- lapply(
  X   = AR,
  FUN = edit_rules
  )

SR <- lapply(
  X   = SR,
  FUN = edit_rules
  )
```

```{r}
save(
  AR, SR,
  file = "App/rules/rules.RDATA"
  )
```

```{r}
filter_rules <- function(rules){

    filter(
       count      >= 10,
       lift       >= 1,
       confidence >= 0.4
      )
}
```

```{r}
AR <- lapply(
  X   = AR,
  FUN = filter_rules
  )

@@

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/Recommender System/rules.RDATA"
  )
```
